Cost- and Deadline-Constrained Provisioning for Scientific Workflow Ensembles in IaaS Clouds

### 2013-04-09 paper/paper.tex
Convert paper to journal format

\documentclass[conference]{IEEEtran}
\usepackage{fancyhdr}
\usepackage[pdftex]{graphicx}
\graphicspath{{./figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm,algpseudocode}
\usepackage{hyperref} % must come before url
\usepackage{url}
\usepackage{color} % for \textcolor
\usepackage{subfig} % for \subfloat

@@

@@

@@

% IEEE Format
\author{\IEEEauthorblockN{Maciej
Malawski\IEEEauthorrefmark{1}\IEEEauthorrefmark{3}, Gideon
Juve\IEEEauthorrefmark{2}, Ewa Deelman\IEEEauthorrefmark{2} and Jarek
Nabrzyski\IEEEauthorrefmark{3}} 
\IEEEauthorblockA{\IEEEauthorrefmark{1}AGH University of Science and
Technology, Dept. of Computer Science, Krakow, Poland, Email:
malawski@agh.edu.pl} 
\IEEEauthorblockA{\IEEEauthorrefmark{2}USC Information Sciences Institute, 4676
Admiralty Way, Marina del Rey, CA, USA, Email: \{gideon,deelman\}@isi.edu} 
\IEEEauthorblockA{\IEEEauthorrefmark{3}University of Notre Dame, Center for
Research Computing, 111 ITC, Notre Dame, IN, USA, Email: naber@nd.edu}
}

% ACM Format
%\numberofauthors{3}
%\author{
%    \alignauthor Maciej Malawski\\
%       \affaddr{AGH University of Science and Technology}\\
%       \affaddr{Dept. of Computer Science}\\
%       \affaddr{Krakow, Poland; and}\\
%       \affaddr{University of Notre Dame}\\
%       \affaddr{Center for Research Computing}\\
%       \affaddr{111 ITC, Notre Dame, IN, USA}\\
%       \email{mmalawsk@nd.edu}
%    \alignauthor Gideon Juve and Ewa Deelman\\
%       \affaddr{USC Information Sciences Institute}\\
%       \affaddr{4676 Admiralty Way}\\
%       \affaddr{Marina del Rey, CA, USA}\\
%       \email{\{gideon,deelman\}@isi.edu}
%    \alignauthor Jarek Nabrzyski\\
%       \affaddr{University of Notre Dame}\\
%       \affaddr{Center for Research Computing}\\
%       \affaddr{111 ITC, Notre Dame, IN, USA}\\
%       \email{naber@nd.edu}
%}

\maketitle

\thispagestyle{fancy}
\lhead{}
\rhead{}
\chead{}
\lfoot{\footnotesize{
SC12, November 10-16, 2012, Salt Lake City, Utah, USA
\newline
978-1-4673-0806-9/12/\$31.00 \copyright 2012 IEEE}}
\rfoot{}
\cfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

@@

% IEEE does not have these
%\category{H.3.4}{Systems and Software}{Distributed systems}
%\category{D.4.8}{Performance}{Simulation}
%\terms{DAG, Scheduling, Simulation}
%\keywords{Scientific workflows, Workflow ensembles, Cloud computing, Infrastructure-as-a-Service}

@@

% IEEE style
\bibliographystyle{IEEEtran}

>>>>

\documentclass[preprint,12pt]{elsarticle}
%\documentclass[final,1p,times,twocolumn]{elsarticle}
\usepackage{fancyhdr}
\usepackage{graphicx}
\graphicspath{{./figures/}}
\DeclareGraphicsExtensions{.pdf,.jpeg,.png}
\usepackage[cmex10]{amsmath}
\usepackage{algorithm,algpseudocode}
\usepackage{hyperref} % must come before url
\usepackage{url}
\usepackage{color} % for \textcolor
\usepackage{subfig} % for \subfloat

@@

\journal{Future Generation Computer Systems}

@@

\begin{frontmatter}

@@

\author[agh]{Maciej Malawski}
\ead{malawski@agh.edu.pl}
\author[isi]{Gideon Juve}
\ead{gideon@isi.edu}
\author[isi]{Ewa Deelman}
\ead{deelman@isi.edu}
\author[nd]{Jarek Nabrzyski}
\ead{naber@nd.edu}

\address[agh]{AGH University of Science and Technology, Dept. of Computer Science, Krakow, Poland} 
\address[isi]{USC Information Sciences Institute, 4676 Admiralty Way, Marina del Rey, CA, USA} 
\address[nd]{University of Notre Dame, Center for Research Computing, 111 ITC, Notre Dame, IN, USA}

@@

\begin{keyword}
scientific workflows, workflow ensembles, cloud computing, resource provisioning
\end{keyword}

\end{frontmatter}

@@

% IEEE style
%\bibliographystyle{IEEEtran}

% FGCS style
\bibliographystyle{elsarticle-num}
